### 2024-07-18 ms.qmd
Updates

There are a total of  `r total_individuals`, and `r total_clutches` clutches in the database. The average number of individuals per clutch is `r mean(individuals_per_clutch)`, with a minimum of `r min(individuals_per_clutch)` individuals per clutch (`r sum(individuals_per_clutch$individual_count == max(individuals_per_clutch$individual_count))` clutches) and a maximum of `r sum(individuals_per_clutch$individual_count == min(individuals_per_clutch$individual_count))` ( clutches).

>>>>

There are a total of  `r total_individuals`, and `r total_clutches` clutches in the database. The average number of individuals per clutch is `r mean(individuals_per_clutch$individual_count)`, with a minimum of `r min(individuals_per_clutch$individual_count)` individuals per clutch (`r sum(individuals_per_clutch$individual_count == min(individuals_per_clutch$individual_count))` clutches) and a maximum of `r max(individuals_per_clutch$individual_count)` (`r sum(individuals_per_clutch$individual_count == max(individuals_per_clutch$individual_count))` clutches). Clutches with only one individual do not contribute to the estimation of within-clutch variability. Including these clutches might lead to misleading variance estimates and convergence issues in the hierarchical model. Therefore, we initially fit the model without the clutch effect to obtain stable estimates at the individual level.
